Brief notes on erosion

### 2019-11-23 docs/proposals/NSF/ProjDocs/funding_BQ.tex
went through entire proposal

\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$383,086 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

>>>>

\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$439,193 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

### 2019-11-23 docs/proposals/NSF/ProjDocs/funding_NM.tex
went through entire proposal

%\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$383,086 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

>>>>

%\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$439,193 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\
